---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---
```{r pkg-knitr-opts, include=FALSE}
hrbrpkghelpr::global_opts()
```

```{r badges, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::stinking_badges()
```

```{r description, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::yank_title_and_description()
```

## What's Inside The Tin

The following functions are implemented:

```{r ingredients, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::describe_ingredients()
```

## Installation

```{r install-ex, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::install_block()
```

## NOTE

Please reference the local [Authorization](authorization.md) documentation or use `vignette("authorization", package="weatherkit")` at an R console for information on how to obtain the necessary authentication and signing components required to use the WeatherKit REST API from this package.

## Usage

```{r lib-ex}
library(weatherkit)

# current version
packageVersion("weatherkit")

```

```{r availability}
wxkit_availability(43.2683199, -70.8635506, "US")
```

```{r weather}
wxkit_weather(43.2683199, -70.8635506) |> 
  str()
```

## weatherkit Metrics

```{r cloc, echo=FALSE}
cloc::cloc_pkg_md()
```

## Code of Conduct

Please note that this project is released with a Contributor Code of Conduct. 
By participating in this project you agree to abide by its terms.
